Monte Carlo and bootstrap for ALL parameters

### 2024-08-13 All_param.Rmd
Began to knit

# res1 <- MonteCarlo(n, 10000)
res1 <- MonteCarlo(n, 10)
# Just one circle to begin with

@@

# res2 <- MC_boot(n, B1 = 1000, B2 = 400)
res2 <- MC_boot(n, B1 = 10, B2 = 4)
# Just one circle to begin with

>>>>

res1 <- MonteCarlo(n, 10000)
# Just one circle to begin with

@@

res2 <- MC_boot(n, B1 = 1000, B2 = 400)
# Just one circle to begin with
